### 2011-06-20 thesis/novelty-intro.tex
cleanup novelty intro.

\subsection{Review of Novelty Detection Methods}
Many approaches have been made based on statistical methods. Those often model
the training data with statistic distributions and then perform hypothesis tests.
For example: testing whether two distributions are the same or using distance to
mean value or quartiles.
In some sense all they define a distance measure to normality and employ a
threshold on that.

A common approach is to use density estimation and use the expected probability
of a sample to classify the sample as novel. Examples of such techniques are
Gaussian Mixture Models and Parzen-window estimators. In order to be effective,
those rely on data as close as possible to the input features and use
dimensionality\hyp{}reduction techniques such as \gls{PCA} to make density
estimation feasible. Note that as dimension increases an exponential number
of data samples would be required to approach the density with the same quality.

>>>>

\subsection{Review of Novelty Detection Methods}
A common approach is to use density estimation and use the expected probability
of a sample to classify the sample as novel. Examples of such techniques are
Gaussian Mixture Models and Parzen-window estimators. In order to be effective,
those rely on data as close as possible to the input features and use
dimensionality\hyp{}reduction techniques such as \gls{PCA} to make density
estimation feasible. Note that as dimension increases an exponential number
of data samples would be required to approach the density with the same quality.
